This is the Title

### 2017-03-15 abc/paper/paper.tex
Some more on the paper; fix typo
Wrote more in paper. Insert diagram in data segment
Write a bunch more, add topclearance param, generalize pdf2ascii a bit, add printer drawing

@@

>>>>

I was kidding when I said the x86 architecture is elegant.

Dr. Dobbs Journal typing in the program

ES segment must be used for IN?

TODO: X86 vs x86

(Idea: ladder is actually interspersed in code, by putting some long instruction
byte (that takes several arguments) before DEC SP JNZ +7e? We can jump directly
to the jump, but if executed in a normal synchronized flow, then it executes some
instruction that does nothing (load immediate?).)

(Idea: Once we've gone past EIP=0xFFFF, we can still execute code from our binary.
It may be possible to get back to CS by doing a jump with the address/operand size prefix?
Neither one has an effect in DOSBox, which may be a bug? Anyway, if an interrupt
is triggered while we're up here, it seems like it only does a 16-bit RET, so that's
kinda busted.)

@@

In video: show error in intel manual http:\\www.intel.com

video: bingo of tom 7 video themes (``retro'', ``alphabet,''
``fractal geometry'')

Ideas for improvement before paper's submitted:
 - Implement 'void' return type
 - Make int literals actually 16 bit for now?
 - Implement multiplication and division
 - Implement switch
 - in paper.c, support multichannel sound.
 - implement sbrk primitive (just returns 0x8000?)
